---
title: "lab2"
author: "cyber-atlas"
date: "February 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1
```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)

ratingHist <- hist(choco$Rating, xlab= "Rating", main="Frequency of Chocolate Ratings", border = 'red' )

?hist
?axis


```

The histogram is skewed left. It seems that the majority of chocolate was rated between 2.5 and 4. The outliers are the subpar chocolates, rated below a 2. 

2 
```{r}
library(ggplot2)
head(choco)
#Making a scatter plot
ggplot(choco, aes(x=choco$Cocoa.Pct, y=choco$Rating)) +
  geom_point(shape=1) +
  geom_smooth()
  #geom_smooth(method=lm)

#Shows us the number of ratings for each cocoa percent 
#table(choco$Cocoa.Pct, choco$Rating)
 
```


According to the data, ratings do depend on cocoa percentage. When the cocoa percentage is below 60% or greateer than 80% then the ratings start to decline. The 60%-80% range is where a majority of the highest ratings lie. It also appears to be the percentage range of cocoa that is most common, would would explain why there are more lower rated chocolates in it. The regression line above shows a decline as the percentages exit that range.

