---
title: "Team"
author: "cyber-atlas, shiffy46"
date: "February 11, 2019"
output: html_document
---


Question Set (team):

1 
```{r}
library(ggplot2)
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
length(choco$Rating)
```
1852 cholate bars were rated.

2 

```{r}

#Plots a barplot showing the number of reviews for each review date
ggplot(data=choco, aes(x=choco$Review.Date))+geom_bar(stat="count")

#If choco review date is 2017, only extract the review date column
#print(choco[choco$Review.Date >= 2017, "Review.Date"])

```

The data is skewed left. The number of ratings increases as the date increases. The number of reatings peaked in 2015. Because 2017 is the most recent date, the data might have been collected in that year, explaining why 2017 has so few reviews.

3

```{r}
table(choco$Rating)
summary(choco$Rating)

#unique(choco$Company.Location)

#Shows the top 3 company locations with the most ratings
showTop3 <- head(sort(table(choco$Company.Location), decreasing=TRUE), 3)
strTop3 <- names(showTop3)
strTop3
#class(strTop3)

usa<- choco[choco$Company.Location == "U.S.A.",]
france<- choco[choco$Company.Location == "France",]
canada<- choco[choco$Company.Location == "Canada",]

boxplot(usa$Rating, france$Rating, canada$Rating, names=strTop3[1:3], ylab="Rating", xlab="Country", main="Rating Distributions by Country", col = c("red", "green", "Gold"))

```

We see that all 3 countries have the same median rating. The distribution of Canada and USA are about the same, while France has a much smaller distribution. USA only has 1 lower outlier, France has 2, and Canada has none. 


4)
We wanted to find the distribution of the 10 specific bean origins based on average ratings.

```{r}
originData<- aggregate(Rating ~ Specific.Bean.Origin, data = choco, mean)
#head(originData[order(-originData$Rating),])
originData <- head(originData[order(-originData$Rating),], 10)
originData

#ggplot(data=originData, aes(x=originData$Specific.Bean.Origin, y=originData$Rating))+geom_histogram(stat = "identity")+coord_cartesian(ylim=c(3.85,4.3))+ylab("Rating")+xlab("Specific Bean Origin")

#Plot a histogram of the ratings and origin
ggplot(data=originData, aes(x=originData$Specific.Bean.Origin, y=originData$Rating))+
  geom_histogram(stat = "identity")+
  coord_flip()+
  ylab("Rating")+
  xlab("Specific Bean Origin")


```


We found that 9 out of the top 10 specific origins are the same average rating at 4.0. This could be due to a lack of ratings or being of similar quality.  


